\boldmath Heavy resonances at energy frontier colliders

### 2018-12-05 paper.tex
removing warnings and updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \ee\ and \mumu final states}
\label{sec:lepee}

Events are required to contain two isolated opposite sign leptons with $\pt > 1$\,TeV, $|\eta|$<4 and an invariant mass $\mll > 2.5$\,TeV.
Figure~\ref{figure:leptonicresonances:masses} (top) shows the invariant mass for a 30\,TeV \ZpSSM\ signal for the $ee$ (left) and $\mu\mu$ (right) channels. The mass resolution is better for the $ee$ channel, as expected from calorimeter constant term. Event yields can be found in Appendix~\ref{app:yields}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_mm.eps}
   \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle.eps}
  \caption{Top: Invariant mass for a 30~TeV signal after full event selection for $ee$ channel (left) and $\mu\mu$ channel (right).
  Bottom: Limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel (left) and luminosity for a $5\sigma$ discovery (right) comparing ee,$\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:masses}
\end{figure}

The di-lepton invariant mass spectrum is used as the discriminant and a 50\% normalisation uncertainty on the background normalisation is assumed.
Figure~\ref{figure:leptonicresonances:resultsll} shows the exclusion limit obtained \intlumifcc\ of data for the $ee$ alone (top left), $\mu\mu$ alone (top right) and combination of (ee,$\mu\mu$) channels (bottom left). Figure~\ref{figure:leptonicresonances:resultsll} (bottom right) shows the integrated luminosity required to reach a $5\sigma$ discovery as a function of the mass of the heavy resonance. The \Zpee\ and \Zpmumu\ channel display very similar performance, due to the low background rates. We conclude therefore that the reference detector design features near to optimal performance for searches involving high \pt\ muon final states.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \tautau\ final state}
\label{sec:leptautau}

At current LHC\CH{add ref}, the most sensitive channel to search for high mass di-$\tau$ resonances is the fully hadronic, and in the following this is what will be considered.
The event selection requires two jets with $p_{T} > 0.5$\,TeV and $|\eta|<2.5$, both identified as $\tau$'s. To ensure no overlap between the $\ell$ and $\tau$ final states, jets containing leptons with $\pt > 100$\,GeV are vetoed. Finally, requirements of $\Delta \phi(\tau_1, \tau_2)> 2$ and $2.5<\Delta R(\tau_1, \tau_2)<4$ are applied to suppress multi-jet background.
Furthermore, mass dependent cuts are applied to maximise the signal significance and are summarised in Table~\ref{tab:leptonicresonances:selectiontautau}. Figure~\ref{figure:leptonicresonances:masses} (right) shows the transverse mass~\footnote{the transverse mass is defined as $m_{T}  =  \sqrt{2\ptZp*\met*(1-cos\Delta\phi(\Zp,\met))} $}
of a 10\,TeV signal. Several proxies for the true resonance mass have been tested, such as the invariant mass of the two $\tau$'s, with and without correction for the missing energy, but the transverse mass provided the best sensitivity and is therefore used to estimate the sensitivity.

Figure~\ref{figure:leptonicresonances:resultstautau} shows the di-$\tau$ transverse mass (left) for a 10\,TeV \ZpSSM, the exclusion limits for 30 ab$^{-1}$ of data (middle) and the required integrated luminosity versus mass of the resonance to reach a $5\sigma$ discovery (right).
The discovery potential for high mass resonances decaying to $\tau\tau$ has been studied using as a benchmark the \ZpSSM\ model. The very large centre of mass energy provides a correspondingly large mass reach. Heavy resonance decaying to $\tau$ leptons reconstructed in the hadronic decay mode are more challenging, but we would be able to probe masses up to 18\,TeV.

\begin{table}[htbp]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
  $4-8$ & > 2.4 & > 2.5 and < 3.5 & > 400 GeV\\
  $10$ & > 2.4 & > 2.7 and < 4 & > 300 GeV\\
  $12-14$ & > 2.6 & > 2.7 and < 4 & > 300 GeV\\
  $16-18$ & > 2.7 & > 2.7 and < 4 & > 300 GeV\\
  $>18$ & > 2.8 & > 3 and < 4 & > 300 GeV\\
  \hline
  \hline
  \end{tabular}
  \caption{List of mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ search.}
  \label{tab:leptonicresonances:selectiontautau}
\end{table}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mt_finalsel_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle.eps}
  \caption{Di-$\tau$ transverse mass (left), limit versus mass for the di-tau channel (center) and luminosity for a $5\sigma$ discovery (right). }
  \label{figure:leptonicresonances:resultstautau}
\end{figure}

@@

Jets are clustered using particle-flow candidates with the anti-$k_T$~\cite{Cacciari:2008gp} algorithm with parameter R=0.4. We require at least two jets with $\pt$>3~TeV and $|\eta<3|$ and the rapidity difference between the two leading jets to be small, $\Delta(\eta)<1.5$ as di-jet events will tend to be more central. The dijet invariant mass of the \qjj\ signal for $m_Q^{*}$ and QCD contributions after the full event selection is shown in Figure~\ref{figure:hadronicresonances:ttsel08} (left).

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf04_sel1_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Qstar_jj_fcc_v02.eps}
 \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_jj_rootStyle.eps}
   \caption{Invariant mass distribution of the two selected jets for a 40~TeV signal (left), limit versus mass (middle) and $5\sigma$ discovery reach.\MS{need editing / style}}
  \label{figure:hadronicresonances:ttsel08}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \ttbar\ final state}
\label{sec:hadtt}

@@

We require two jets with a $\pt$>3~TeV and $|\eta<3|$ and $\Delta(\eta)<2.4$. Both jets must either be $W$ or top tagged (section~\ref{subsec:mvatagger}) by requiring multivariate tagger > 0.15. Both high-\pt\ jets must be $b$-tagged for the \Zptt\ analysis. Finally, to further reject QCD, we require for both jets $m_{SD}>40$~GeV. In Figure~\ref{figure:hadronicresonances:ttsel08} we show the di-jet invariant mass distribution after the final cuts for the \rsg\ (center) and \Zptt\ (right) analyses respectively.

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_fit_sel4_nostack_log.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tt_SSM_TC2_tagger_TRFbtag_rootStyle.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tt_fcc_v02.eps}
  \caption{Invariant mass distribution of the two leading jets for the pre-selection (left) and full selection (right) for a 40~TeV signal for the \qjj\ (left), and a 20~TeV signal for \rsg\ (center) and \Zptt\ (right) analyses.\MS{need editing / style}}
  \label{figure:hadronicresonances:ttsel08}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \ww\ final state}
\label{sec:hadww}

The di-jet invariant mass is used as a discriminant. In order to reduce large statistical fluctuations from high Monte Carlo weight events, we parameterize the background invariant mass distribution with the following function (conservatively assuming 50\% uncertainty on the background normalisation) $f(z)=p_1(1-z)^{p_2}z^{p_3}z^{p_{4}logz}$, where $z=m_{jj}/\sqrt{s}$.

The expected exclusion limits at 95\% CL are shown in Figures~\ref{figure:hadronicresonances:limits} and~\ref{figure:hadronicresonances:resultsjj}. For the \qjj\ masses up to 40~TeV could be discovered with \intlumifcc. Reconstructing Heavy resonances decaying to $WW$ and \ttbar\ is more challenging and requires the use of novel approaches to boosted object tagging to reduce the backgrounds. The reach for \Zptt\ (in TC2 models) and \rsg\ is 24~TeV and 22~TeV respectively and it is possible to discover a $Z^{\prime}_{SSM} \rightarrow \ttbar$ up to $m_{Z}=18$~TeV.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_MetCorr_fit_sel8_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_RSGraviton_ww_fcc_v02.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ww_tagger_rootStyle.eps}
  \caption{Invariant mass distribution of the two leading jets for the pre-selection (left) and full selection (right) for a 40~TeV signal for the \qjj\ (left), and a 20~TeV signal for \rsg\ (center) and \Zptt\ (right) analyses.\MS{need editing / style}}
  \label{figure:hadronicresonances:ttsel08}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with 27\,TeV HE-LHC}
\label{sec:ana27tev}
The search for heavy resonances have also been study at the 27\,TeV HE-LHC. The analyses strategies remains identical to what was already presented, to the only difference that thresholds have been re-optimised to accommodate for the lower center of mass energy. The changes can be summarised as follows:
\begin{itemize}
\item \Zpee\ or \Zpmumu : leton $p_T$ lowered from 1 to 0.5\,TeV
%\item \Zpmumu\ f.a. and t-channel LQ : leton $p_T$ lowered from  1.2 TeV to 0.75 TeV
\item \Zptata\ : mass dependent cuts changed as shown in Table~\ref{tab:leptonicresonances:selectiontautau27}
\item \rsg, \Zptt, \qjj\ : jet $p_T$ lowered from 3 to 1\,TeV
\end{itemize}

\begin{table}[htbp]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
   $2$ & > 2.4 & > 2.4 and < 3.9 & > 80 GeV\\
   $4$ & > 2.4 & > 2.7 and < 4.4 & > 80 GeV\\
   $6$ & > 2.4 & > 2.9 and < 4.4 & > 80 GeV\\
   $8$ & > 2.6 & > 2.9 and < 4.6 & > 80 GeV\\
  $10$ & > 2.8 & > 2.9 and < 4.1 & > 60 GeV\\
  $12$ & > 2.8 & > 3.0 and < 3.6 & > 60 GeV\\
  $14$ & > 3.0 & > 3.0 and < 3.3 & > 60 GeV\\
  \hline
  \hline
  \end{tabular}
  \caption{Mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ resonance search.}
  \label{tab:leptonicresonances:selectiontautau27}
\end{table}

\begin{table}[!htb]\centering
\begin{tabular}{|c|c|c|c|}
\hline
\hline
analysis   & \multicolumn{3}{c|}{HE-LHC (FCC-hh)} \\
           & Limit [TeV] & Disco [TeV]   & Disco [TeV] \\
           &             & 1 (2.5) $ab^{-1}$ & 15 (30) $ab^{-1}$ \\
\hline
\Zpee+\Zpmumu & 13 (40) & 10 (33) & 13 (43) \\
\Zptata       &  6 (14) &  3 (12) &  6 (18) \\
\Zpmumu\ f.a. &  4 (25) &  - (10) &  2 (19) \\
\Zptt         & 10 (28) &  6 (16) &  8 (23) \\
\rsg          &  8 (28) &  5 (15) &  7 (22) \\
\qjj          & 14 (43) & 10 (36) & 12 (40) \\
\hline
\hline
\end{tabular}
\caption{Limit and discovery reach at 5 $\sigma$ comparison between HE-LHC (27 TeV 15 ab-1) and FCC-hh (100 TeV 30 ab-1).}
\label{tab:27vs100}
\end{table}

@@

The potential for discriminating various $Z'$ models is first investigated using the leptonic $ee$ and $\mu\mu$ final states only. The signal samples for the 6 models and the Drell-Yan backgrounds have been generated with \py~\cite{Sjostrand:2014zea} including the interference between the signal and background. The $Z'$ decays assume lepton flavour universality. For a description of the event selection and a discussion of the discovery potential in leptonic final states for the list of $Z'$ models being discussed here, the reader should refer to Section~\cite{subsubsec:hr_lep}. We simply point out here that with \intlumihelhc\,, all $Z'$ models with $m_{Z'}~\lesssim~10$~TeV can be excluded at \sqrtshelhc.

@@

Model discrimination can be improved by including an analysis involving three $Z'$ addition hadronic final states: $t\bar{t}$, $b\bar{b}$ and $q\bar{q}$, where $q=u,d,c,s$. The sample production and event selection for the $t\bar{t}$, $q\bar{q}$ final states has been described to some extent in Section~\cite{subsubsec:hr_had}. We simply remind the reader that the analysis involves requiring the presence of two central high $\pt$ jets. In order to ensure complete orthogonality between the various final states, jets are required to be tagged as follows. In the $Z' \rightarrow t\bar{t}$ analysis both jets should be \emph{top-tagged}. For the $Z' \rightarrow b\bar{b}$ final state both jets are required to be \emph{b-tagged} and we veto events containing at least one top-tagged jet. Finally, in the $Z' \rightarrow q\bar{q}$ analysis, we veto events that contain at least one b-tagged or top-tagged jet.

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multivariate object tagger}
\label{sec:app:mva}
The training samples are built from jets that do not contain leptons, for example from sem-leptonic b-decays.
The BDT parameters used are the following : NTrees=600, MaxDepth=4, AdaBoost, AdaBoostBeta=0.15, SeparationType=GiniIndex, nCuts=100, PruneMethod=NoPruning.
As an example, the $E_{F}(n=1,\alpha=0.05)$ observable is shown in Figures~\ref{fig:TMVA_final_result} left.
The evolution of the light jet efficiency versus the $W$ and top tagging efficiencies for both taggers is shown in Figure~\ref{fig:TMVA_final_result} right.
Cross-checks have been performed to further validate the procedure. First, by removing highly correlated variables, such as \CH{@David Add example}, it showed the same performances \CH{@ David, then why don't we remove the correlated variables?}.
As a second test, the BDT response has been tested for different signal masses to understand how the mass dependence could affect the analyses (Figure \ref{fig:BDT_signal_shape_comparison}). For the cut used in the analysis (BDT score greater than 0.15), the shape of the BDT is not dramatically changing the signal efficiency.% and it removes 90\% and 95\% of light jets for thad and Whad taggers respectively.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texorpdfstring{\ee}{ee} and \texorpdfstring{\mumu}{mumu} final states}
\label{sec:lepee}

Events are required to contain two isolated opposite sign leptons with $\pt > 1$\,TeV, $|\eta|$<4 and an invariant mass $\mll > 2.5$\,TeV.
Figure~\ref{figure:leptonicresonances:ll} (top) shows the invariant mass for a 30\,TeV \ZpSSM\ signal for the $ee$ (left) and $\mu\mu$ (right) channels. The mass resolution is better for the $ee$ channel, as expected from calorimeter constant term. Event yields can be found in Appendix~\ref{app:yields}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_mm.eps}
   \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle.eps}
  \caption{Top: Invariant mass for a 30~TeV signal after full event selection for $ee$ channel (left) and $\mu\mu$ channel (right).
  Bottom: Limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel (left) and luminosity for a $5\sigma$ discovery (right) comparing ee,$\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:ll}
\end{figure}

The di-lepton invariant mass spectrum is used as the discriminant and a 50\% normalisation uncertainty on the background normalisation is assumed.
Figure~\ref{figure:leptonicresonances:ll} shows the exclusion limit obtained \intlumifcc\ of data for the $ee$ alone (top left), $\mu\mu$ alone (top right) and combination of (ee,$\mu\mu$) channels (bottom left). Figure~\ref{figure:leptonicresonances:ll} (bottom right) shows the integrated luminosity required to reach a $5\sigma$ discovery as a function of the mass of the heavy resonance. The \Zpee\ and \Zpmumu\ channel display very similar performance, due to the low background rates. We conclude therefore that the reference detector design features near to optimal performance for searches involving high \pt\ muon final states.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texorpdfstring{\tautau}{tautau} final state}
\label{sec:leptautau}

At current LHC\CH{add ref}, the most sensitive channel to search for high mass di-$\tau$ resonances is the fully hadronic, and in the following this is what will be considered.
The event selection requires two jets with $p_{T} > 0.5$\,TeV and $|\eta|<2.5$, both identified as $\tau$'s. To ensure no overlap between the $\ell$ and $\tau$ final states, jets containing leptons with $\pt > 100$\,GeV are vetoed. Finally, requirements of $\Delta \phi(\tau_1, \tau_2)> 2$ and $2.5<\Delta R(\tau_1, \tau_2)<4$ are applied to suppress multi-jet background.
Furthermore, mass dependent cuts are applied to maximise the signal significance and are summarised in Table~\ref{tab:leptonicresonances:tautau}. Figure~\ref{figure:leptonicresonances:tautau} (right) shows the transverse mass~\footnote{the transverse mass is defined as $m_{T}  =  \sqrt{2\ptZp*\met*(1-cos\Delta\phi(\Zp,\met))} $}
of a 10\,TeV signal. Several proxies for the true resonance mass have been tested, such as the invariant mass of the two $\tau$'s, with and without correction for the missing energy, but the transverse mass provided the best sensitivity and is therefore used to estimate the sensitivity.

Figure~\ref{figure:leptonicresonances:tautau} shows the di-$\tau$ transverse mass (left) for a 10\,TeV \ZpSSM, the exclusion limits for 30 ab$^{-1}$ of data (middle) and the required integrated luminosity versus mass of the resonance to reach a $5\sigma$ discovery (right).
The discovery potential for high mass resonances decaying to $\tau\tau$ has been studied using as a benchmark the \ZpSSM\ model. The very large centre of mass energy provides a correspondingly large mass reach. Heavy resonance decaying to $\tau$ leptons reconstructed in the hadronic decay mode are more challenging, but we would be able to probe masses up to 18\,TeV.

\begin{table}[htbp]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
  $4-8$ & > 2.4 & > 2.5 and < 3.5 & > 400 GeV\\
  $10$ & > 2.4 & > 2.7 and < 4 & > 300 GeV\\
  $12-14$ & > 2.6 & > 2.7 and < 4 & > 300 GeV\\
  $16-18$ & > 2.7 & > 2.7 and < 4 & > 300 GeV\\
  $>18$ & > 2.8 & > 3 and < 4 & > 300 GeV\\
  \hline
  \hline
  \end{tabular}
  \caption{List of mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ search.}
  \label{tab:leptonicresonances:tautau}
\end{table}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mt_finalsel_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle.eps}
  \caption{Di-$\tau$ transverse mass (left), limit versus mass for the di-tau channel (center) and luminosity for a $5\sigma$ discovery (right). }
  \label{figure:leptonicresonances:tautau}
\end{figure}

@@

Jets are clustered using particle-flow candidates with the anti-$k_T$~\cite{Cacciari:2008gp} algorithm with parameter R=0.4. We require at least two jets with $\pt$>3~TeV and $|\eta<3|$ and the rapidity difference between the two leading jets to be small, $\Delta(\eta)<1.5$ as di-jet events will tend to be more central. The dijet invariant mass of the \qjj\ signal for $m_Q^{*}$ and QCD contributions after the full event selection is shown in Figure~\ref{figure:hadronicresonances:jj} (left).
For the \qjj\ masses up to 40~TeV could be discovered with \intlumifcc.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf04_sel1_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Qstar_jj_fcc_v02.eps}
 \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_jj_rootStyle.eps}
   \caption{Invariant mass distribution of the two selected jets for a 40~TeV signal (left), limit versus mass (middle) and $5\sigma$ discovery reach.\MS{need editing / style}}
  \label{figure:hadronicresonances:jj}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texorpdfstring{\ttbar}{tt} final state}
\label{sec:hadtt}

@@

We require two jets with a $\pt$>3~TeV and $|\eta<3|$ and $\Delta(\eta)<2.4$. Both jets must either be $W$ or top tagged (section~\ref{subsec:mvatagger}) by requiring multivariate tagger > 0.15. Both high-\pt\ jets must be $b$-tagged for the \Zptt\ analysis. Finally, to further reject QCD, we require for both jets $m_{SD}>40$~GeV. In Figure~\ref{figure:hadronicresonances:tt} we show the di-jet invariant mass distribution after the final cuts for the \rsg\ (center) and \Zptt\ (right) analyses respectively.

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_fit_sel4_nostack_log.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tt_SSM_TC2_tagger_TRFbtag_rootStyle.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tt_fcc_v02.eps}
  \caption{Invariant mass distribution of the two leading jets for the pre-selection (left) and full selection (right) for a 40~TeV signal for the \qjj\ (left), and a 20~TeV signal for \rsg\ (center) and \Zptt\ (right) analyses.\MS{need editing / style}}
  \label{figure:hadronicresonances:tt}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texorpdfstring{\ww}{ww} final state}
\label{sec:hadww}

The expected exclusion limits at 95\% CL are shown in Figures~\ref{figure:hadronicresonances:ww}. For the \qjj\ masses up to 40~TeV could be discovered with \intlumifcc. Reconstructing Heavy resonances decaying to $WW$ and \ttbar\ is more challenging and requires the use of novel approaches to boosted object tagging to reduce the backgrounds. The reach for \Zptt\ (in TC2 models) and \rsg\ is 24~TeV and 22~TeV respectively and it is possible to discover a $Z^{\prime}_{SSM} \rightarrow \ttbar$ up to $m_{Z}=18$~TeV.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_MetCorr_fit_sel8_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_RSGraviton_ww_fcc_v02.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ww_tagger_rootStyle.eps}
  \caption{Invariant mass distribution of the two leading jets for the pre-selection (left) and full selection (right) for a 40~TeV signal for the \qjj\ (left), and a 20~TeV signal for \rsg\ (center) and \Zptt\ (right) analyses.\MS{need editing / style}}
  \label{figure:hadronicresonances:ww}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with 27 TeV HE-LHC}
\label{sec:ana27tev}
The search for heavy resonances have also been study at the 27\,TeV HE-LHC. The analyses strategies remains identical to what was already presented, to the only difference that thresholds have been re-optimised to accommodate for the lower center of mass energy. The changes can be summarised as follows:
\begin{itemize}
\item \Zpee\ or \Zpmumu : leton $p_T$ lowered from 1 to 0.5\,TeV
%\item \Zpmumu\ f.a. and t-channel LQ : leton $p_T$ lowered from  1.2 TeV to 0.75 TeV
\item \Zptata\ : mass dependent cuts changed as shown in Table~\ref{tab:leptonicresonances:tautau27}
\item \rsg, \Zptt, \qjj\ : jet $p_T$ lowered from 3 to 1\,TeV
\end{itemize}

The results are summarised in Table~\ref{tab:27vs100}, together with a comparison to FCC-hh.

\begin{table}[htbp]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
   $2$ & > 2.4 & > 2.4 and < 3.9 & > 80 GeV\\
   $4$ & > 2.4 & > 2.7 and < 4.4 & > 80 GeV\\
   $6$ & > 2.4 & > 2.9 and < 4.4 & > 80 GeV\\
   $8$ & > 2.6 & > 2.9 and < 4.6 & > 80 GeV\\
  $10$ & > 2.8 & > 2.9 and < 4.1 & > 60 GeV\\
  $12$ & > 2.8 & > 3.0 and < 3.6 & > 60 GeV\\
  $14$ & > 3.0 & > 3.0 and < 3.3 & > 60 GeV\\
  \hline
  \hline
  \end{tabular}
  \caption{Mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ resonance search.}
  \label{tab:leptonicresonances:tautau27}
\end{table}

\begin{table}[!htb]\centering
\begin{tabular}{|l|c|c|c|}
\hline
\hline
analysis   & \multicolumn{3}{c|}{HE-LHC (FCC-hh)} \\
           & Limit [TeV] & Disco [TeV]   & Disco [TeV] \\
           &  15 (30) ab$^{-1}$ & 1 (2.5) ab$^{-1}$ & 15 (30) ab$^{-1}$ \\
\hline
\Zpll\ (l=e,$\mu$) & 13 (40) & 10 (33) & 13 (43) \\
\Zptata       &  6 (14) &  3 (12) &  6 (18) \\
%\Zpmumu\ f.a. &  4 (25) &  - (10) &  2 (19) \\
\Zptt         & 10 (28) &  6 (16) &  8 (23) \\
\rsg          &  8 (28) &  5 (15) &  7 (22) \\
\qjj          & 14 (43) & 10 (36) & 12 (40) \\
\hline
\hline
\end{tabular}
\caption{Limit and discovery reach at 5 $\sigma$ comparison between HE-LHC and FCC-hh.}
\label{tab:27vs100}
\end{table}

@@

The potential for discriminating various $Z'$ models is first investigated using the leptonic $ee$ and $\mu\mu$ final states only. The signal samples for the 6 models and the Drell-Yan backgrounds have been generated with \py~\cite{Sjostrand:2014zea} including the interference between the signal and background. The $Z'$ decays assume lepton flavour universality. For a description of the event selection and a discussion of the discovery potential in leptonic final states for the list of $Z'$ models being discussed here, the reader should refer to Section~\ref{sec:lep}. We simply point out here that with \intlumihelhc\,, all $Z'$ models with $m_{Z'}~\lesssim~10$~TeV can be excluded at \sqrtshelhc.

@@

Model discrimination can be improved by including an analysis involving three $Z'$ addition hadronic final states: $t\bar{t}$, $b\bar{b}$ and $q\bar{q}$, where $q=u,d,c,s$. The sample production and event selection for the $t\bar{t}$, $q\bar{q}$ final states has been described to some extent in Section~\ref{sec:hadronic}. We simply remind the reader that the analysis involves requiring the presence of two central high $\pt$ jets. In order to ensure complete orthogonality between the various final states, jets are required to be tagged as follows. In the $Z' \rightarrow t\bar{t}$ analysis both jets should be \emph{top-tagged}. For the $Z' \rightarrow b\bar{b}$ final state both jets are required to be \emph{b-tagged} and we veto events containing at least one top-tagged jet. Finally, in the $Z' \rightarrow q\bar{q}$ analysis, we veto events that contain at least one b-tagged or top-tagged jet.

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multivariate object tagger}
\label{sec:app:mva}
The training samples are built from jets that do not contain leptons, for example from sem-leptonic b-decays.
The BDT parameters used are the following : NTrees=600, MaxDepth=4, AdaBoost, AdaBoostBeta=0.15, SeparationType=GiniIndex, nCuts=100, PruneMethod=NoPruning.
As an example, the $E_{F}(n=1,\alpha=0.05)$ observable is shown in Figures~\ref{fig:TMVA_final_result} left.
The evolution of the light jet efficiency versus the $W$ and top tagging efficiencies for both taggers is shown in Figure~\ref{fig:TMVA_final_result} right.
Cross-checks have been performed to further validate the procedure. First, by removing highly correlated variables, such as \CH{@David Add example}, it showed the same performances \CH{@ David, then why don't we remove the correlated variables?}.
As a second test, the BDT response has been tested for different signal masses to understand how the mass dependence could affect the analyses. For the cut used in the analysis (BDT score greater than 0.15), the shape of the BDT is not dramatically changing the signal efficiency.% and it removes 90\% and 95\% of light jets for thad and Whad taggers respectively.
